R Notebook

### 2017-07-06 doc/RMD/wmn-differentiation.Rmd
don't print whole friggen table :zap:

dists <- bind_rows(`White Mold Nurseries` = wmn_distance, 
                   `Between` = inter_distance,
                   `Other Sources` = nwmn_distance, 
                   .id = "Comparison") %>%
  mutate(Comparison = forcats::fct_inorder(Comparison))
dists
ggplot(dists, aes(y = distance, x = Comparison, fill = Comparison)) +
  geom_violin() +
  geom_boxplot(width = 0.25) +
  scale_fill_manual(values =  c(`Other Sources` = "grey35", `White Mold Nurseries` = "grey95", Between = "grey65")) +
  scale_color_manual(values = c(`Other Sources` = "grey35", `White Mold Nurseries` = "grey95", Between = "grey65")) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  theme(axis.text = element_text(color = "black")) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  ylab("Bruvo's Distance")
```

>>>>

dists <- bind_rows(`White Mold Nurseries` = wmn_distance, 
                   `Between` = inter_distance,
                   `Other Sources` = nwmn_distance, 
                   .id = "Comparison") %>%
  mutate(Comparison = forcats::fct_inorder(Comparison)) %>%
  as_tibble()
dists
ggplot(dists, aes(y = distance, x = Comparison, fill = Comparison)) +
  geom_violin() +
  geom_boxplot(width = 0.25) +
  scale_fill_manual(values =  c(`Other Sources` = "grey35", `White Mold Nurseries` = "grey95", Between = "grey65")) +
  scale_color_manual(values = c(`Other Sources` = "grey35", `White Mold Nurseries` = "grey95", Between = "grey65")) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  theme(axis.text = element_text(color = "black")) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  ylab("Bruvo's Distance")
```
